---
title       : Urban Population Growth
subtitle    : Project presentation
author      : Justin Rice
job         : System Developer
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

This presentation is being used used as a part of my analysis of World Bank's Climate Change Data. The analysis is a rather simple one. It allows the user to use sliders to filter the data.
The app can be found here:

https://ricej2.shinyapps.io/UrbanGrowth/

--- .class #id 

## App Layout
The app has a tabular panel which has 2 sub panels. The first sub panel is simply the data as a table. The second panel shows the summary of the Urban Growth according to the current filters.

---

## Data Sample

Here is a sample of what the data looks like:
```{r}
growthData <- read.csv("../ClimateIndicators.csv")
str(growthData[,2:9])
```


---

## Frequencies

Here we can see that the data is pretty skewed.
```{r}
table(growthData[,9])
```